A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-11 paper.tex
write in method

LTC会记录一个范围，from which 可以找到一条直线，代替original data，并且保证 保证度，或者 distort。 当一个新data来的时候，base data会与 data+/-EPSILON 创建一个 临时的范围， 如果这个范围与 已经记录的范围 存在 交集，那么更新已记录的范围， 如果交集为空，则transmit base data，并将，已经记录的范围的median，and current timesamp - 1 作为 base point的值和timestamp. 以此循环。
画个图。
只需要 constant Memory。

@@

In practice, It's needed to transmit raw data which has multi-parameters to clients e.g. Accelerometer, Euler Angle and Magnetometer etc. Most of 以前的 paper just force on single dimension sensor data Compression. **** . So we purpose a method to compress multi-dimensional sensor data named LTC-D. It is used as linear estimation method. Same as usual estimation compression method,  distance(different) with compressed data from LTC-D and original data would not exceed the predefined error range. We need to find line to represent original data, it means the lines
pass through datas' error range. But in stream data, time seires data, it is difficult, because all data do not show in same time plane. So this method will mapping all data into one time plane. Then for each mapped error range of data, check if there is intersection among them. If so means there is a line could represent original data, and vice versa.

The method as below: assume the stream $i_{th}$ data $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$ in our Method. 通常设置 base point之后的一个时间节点作为mapping节点. We also need to record the intersect S for find result lines. 我们确定以 base point 之后的第一个时间节点， 作为mapping的目标节点，再在 The first data D_1 would change into tolerance range R_1. 我们 set S = R_1. For each follow data D_i i>1, mapping D_1 into hat(D_1) = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$, and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$.
the tolerance range after R_i, intersect with S, if there is overlap, update S = S 交 R_i. If not, the base point would be transmited and select a point in S as base point with timestamp t_{i-1}.

@@

对于 误差范围，会根据EPSILON 改变，也会根据我们设定的 data 与 EPSILON 的 不同类型的距离有关系。

如果使用 Manhattan的话 误差范围 会变成 RequirePackagectangle or cube for 2d and 3d respectively. 就是 EPSILON*sqrt(d)  图
如果使用 Euclidean的话 误差范围 会变成 disk or ball 分别是 2d, 3d， 保持 EPSILON.图

我们用2d Manhattan 来做例子。 画图

@@

\section{Implementation}
Our code is available at ... (make a clean release!)

\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
After that updating tolerance range by adding designed error margin which after mapping
$\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same time-stamp. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
画图；
写一个3-D的例子，并解释一下 算法
assume 有一个 3D 的数据 (x,y,z, t_n)， 会被mapping到 (....) with error sphere EPSILON/(t_n - t_1).and check if there is public intersection with list of circle which recorded.
首先确定x的范围，C_maxX = Min=1.n(c_i.x + E/i), C_minX = Max=1.n(c_i.x - E/i), if C_maxX < C_minX, means there is no public intersection amount those circles.
after that 使用二分法 mid_x=(C_maxX + C_minX)/2, with x=mid_x computer bounding range of y-axis, 并对y轴继续使用 二分法，在z-axis 上计算 C_minZ and C_maxZ, 如果 C_maxZ > C_minZ 说明 在x=mid_x, y=mid_y 这条线上 存在一个或多个点 在intersection amount those circles. so 我们可以确认 确认交集的存在，并且 把点(mid_x, mid_y, mid_z) 保存下来，以便将来更新base point. 在这个算法中 第一次遍历circle 得到maxX maxY 需要 O(n) 然后 二分法O(lgn) 进入循环, 之后 O(n) 遍历，在二分法 mid_y, 进入循环之后需要O(n) 遍历circle 得到 max_z and min_z 所以 复杂度是 O(n) + O(lgn)*(O(n) + O(lgn)*O(n)) = O(lgn lgn n)

通过这个 例子 我们可以把 3-D 延伸到 n-D。

In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.
\begin{algorithm}
    \caption{whether disks intersect}
    \begin{flushleft}
        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\
        \textbf{function} isIntersect$(l, d, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \STATE $tmp_list \gets null$
        \STATE $max\_x\gets d.x+d.r$
        \STATE $min\_x\gets d.x-d.r$

        \FORALL{$old\_disk$ \textbf{in} $l$}
            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
                \STATE \textbf{return} false
            \ELSIF{$d \cap old\_disk \neq d$}
                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
            \ENDIF
        \ENDFOR
        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
        \IF{$max\_x < min\_x$}
            \STATE \textbf{return} false
        \ENDIF
        \WHILE{$min\_x \leqslant max\_x$}
            \STATE $mid \gets (min\_x + max\_x)/2$
            \STATE $max\_y \gets +\infty$
            \STATE $min\_y \gets -\infty$
            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
                \IF{$P_1.y < max\_y$}
                    \STATE $max\_y \gets p_1.y$
                    \STATE $max\_index \gets i$
                \ENDIF
                \IF{$P_2.y > min\_y$}
                    \STATE $min\_y \gets p_2.y$
                    \STATE $min\_index \gets i$
                \ENDIF
            \ENDFOR
            \IF{$max\_y >= min\_y$}
                \STATE $p.x \gets mid$
                \STATE $p.y \gets (max\_y+min\_y)/2$
                \STATE $l \gets tmp\_list$
                \STATE \textbf{return} true
            \ENDIF
            \STATE {Assume $P_d$ is the intersection between line of
            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
            , and their common chord}
            \IF{$P_d.x < mid$}
                \STATE $max\_y \gets mid-1$
            \ELSIF{$P_d.x > mid$}
                \STATE $min\_y \gets mid+1$
            \ENDIF
        \ENDWHILE
        \RETURN false
    \end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
    \caption{whether intersect  for n dimension}
    \begin{flushleft}
        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
        \textbf{Output:} $true|false$  is there a intersection\\
        \textbf{function} isIntersect$(l, o, p)$
    \end{flushleft}
    \begin{algorithmic}[1]
        \STATE $tmp_list \gets null$
        \STATE $max \gets o.d\_n+o.r$
        \STATE $min \gets o.d\_n-o.r$

        \FORALL{$old\_obj$ \textbf{in} $l$}
            \IF{$o \cap old\_obj = \emptyset$}
                \STATE \textbf{return} false
            \ELSIF{$o \cap old\_obj \neq o$}
                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
            \ENDIF
        \ENDFOR
        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
        \IF{$max < min$}
            \STATE \textbf{return} false
        \ENDIF
        $p\_cp \gets p$
        \IF{Recursive$(min, max, n, p\_cp)$}
            \STATE $p \gets p\_cp$
            \STATE \textbf{return} true
        \ELSE
            \STATE \textbf{return} false
        \ENDIF
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \begin{flushleft}
        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
    \end{flushleft}
    \begin{algorithmic}[1]
        \WHILE{$left \leqslant right$}
            \STATE $mid \gets (left + right)/2$
            \STATE $max \gets +\infty$
            \STATE $min \gets -\infty$
            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
                \IF{$P_1.d_{j-1} < max$}
                    \STATE $max \gets p_1.d_{j-1}$
                    \STATE $max\_index \gets i$
                \ENDIF
                \IF{$P_2.d_{j-1} > min$}
                    \STATE $min \gets p_2.d_{j-1}$
                    \STATE $min\_index \gets i$
                \ENDIF
            \ENDFOR
            \IF{$max >= min$}
                \STATE $p.d_j \gets mid$
                \IF{Recursive$(min, max, j-1, p)$}
                    \STATE \textbf{return} true
                \ENDIF
            \ENDIF
            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
            \IF{$P_d.d_j < mid$}
                \STATE $right \gets mid-1$
            \ELSIF{$P_d.d_j > mid$}
                \STATE $left \gets mid+1$
            \ENDIF

        \ENDWHILE
        \RETURN false
    \end{algorithmic}
\end{algorithm}

>>>>

@@

In practice, It's needed to transmit raw data which has multi-parameters
to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
Most of previous paper just force on single dimension sensor
data Compression. So we purpose a method to compress multi-dimensional
sensor data named LTC-D. It is used as linear estimation method.
Same as usual estimation compression method,  distance(different)
with compressed data from LTC-D and original data would not exceed
the predefined error range. We need to find line to represent
original data, it means the lines pass through datas' error range.
But in stream data, time seires data, it is difficult, because
all data do not show in same time plane. So this method will
mapping all data into one time plane. Then for each mapped error
range of data, check if there is intersection among them. If so means
there is a line could represent original data, and vice versa.

The method as below: assume the stream $i_{th}$ data
$D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
As usual, the timestamp after basepoint would be set as mapping plane.
We also need to record the intersect $S$ for find result lines.
The first data $D_1$ would change into tolerance range $R_1$.
initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
with S, if there is overlap, update S = S intersect R_i. If not, the base point
would be transmited and select a point in S as base point with timestamp $t_{i-1}$.

@@

for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
\todo{maybe need a graphic}

@@

\section{Implementation}
Our code is available at ... (make a clean release!)
/todo{below content is useful? }
\subsection{Multidimensional LTC with Manhattan distance}
In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively. But we did some changes in our method. Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$. cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
After that updating tolerance range by adding designed error margin which after mapping
$\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.

@@

\subsection{Multidimensional LTC with Euclidean distance}
In Euclidean distance version, we also map the coming data into same time-stamp $t_1$ the timestamp after base point. The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension. In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them. For instance, in 3D-t, assume we have a the base point $Z = D_0$ and the tolerance range $R_1$ which is a ball as the intersection S. we need a list L to record mapped balls from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping this data into $t_1$, and add it into list. Then the work is check out if all balls intersect, and form a public intersection. The method is based on plane sweep and binary search. At first, select one parameter, such as x-axis, finding a bounding range of all balls $B_i$ in x-axis. suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap among balls, then the axis of the points inside intersection must located between Min_bound_x and Max_bound_x. Using binary search to select mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding with the plane x = mid_x. If the get bounding range in y-axis where $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, parallels z-axis, could pass through all balls. Finally, in z-axis, compute bounding range, and If $Max_bound_z > Min_bound_z$, there must be one or more points inside all balls. The problem be solved. If the loop of binary search in x-axis overs, then there is no public intersection among balls, and need to transmit and update base point. In this method we need O(n*logn*logn) time complexity for binary search in x-axis and y-axis and traversal all balls in z-axis, also O(n) space complexity is needed for maintaining list. According this method, it could be extended into N-dimensional data. The main idea is to search, dimension by dimension, from a room or plane or line and get intersection point finally.

/todo{below content is useful? }
In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
\begin{itemize}
\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk. After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data. Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis. So In 3-dimension whether \textit{n} balls intersect need to be check.
\end{itemize}

At first, let us solve the \textit{n} disks intersect. We use a algorithm which is based on plane sweep and dichotomy. Assume a disk include center$(x,y)$ and radius $r$. The pseudo-code in Algorithm 1.

@@
